Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-14 paper/paper.tex
pass on section III

@@

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of functions from standard JS
libraries.
\Mar{what is that exactly? can we cite? is that only spec or
actually code as most of java.* libraries.}
\Igor{seems like an API. They define the language behavior; grammar;
values to static variables; the methods for each "class"(Object)...
These irregularities appears on engine implementation, 
maybe an wrong if statement and so on.}
We found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the
engine developers}\Mar{If you confirm that there is no code in specs
  (see comment above), what would be those abstract
  functions/interfaces that you mentioned to me the other day?}.
\Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that,
the function \CodeIn{Number.toPrecision(precision)}, in general,
if precision is defined the method returns a String 
containing the Number value represented either 
in decimal exponential notation or in decimal 
fixed notation~\cite{es6-toPrecision}. The Number object uses a 
property that the specification describes as approximately so when we use 
toPrecision with a bigger precision, the values of each engine may vary, this
could be considered as a case of incompatibility by engine design.}
In those cases, our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only \Fix{12\%} of the reals bugs
we found originated from the LO category.
\Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
due the capacity of a fuzzer add an infinite repetition statement. We expected that
each test process can running utmost 5 seconds, if exceed this condition we stop 
the process and add a output message of a TIMEOUT error.}

\Mar{show real examples of
  HI and LO. Use the stacktraces to explain what is going on.}

\Igor{
  We defined if a warning is in HI or LO group according to console output.
  The error stream in the output shows relevant informations that we can 
  process. The Figure~\ref{fig:error-output} shows examples of HI and LO warning
  outputs based on the stream output came from Chakra engine. 
  % The error message shows informations related to the assertion code (see at line 2) 
  % that thows an Error exception. This case was considered as HI groups and after 
  % several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
}

@@

\Mar{can we detect dups mining issue trackers?}
\Igor{
  acho que encontrar duplicatas seria um estudo a parte, devido a linguagem natural.
  Tenho umas consideracoes:
  \begin{itemize}
    \item warning HI possui a msg "Error: Test Failed", nao tem como buscar algo com isso, 
    se for pegar a linha que falhou, provavelmente vai mostrar a linha onde o assert se encontra.
    \item warning LO: podemos tentar conseguir buscar pelo output/funcao que falhou,
    \item O fuzzinator tem algo similar (dei uma olhada rapida, nao eh complicado)
  \end{itemize}
}

>>>>

\Mar{what is that exactly? can we cite? is that only spec or actually
  code as most of java.* libraries.}  \Igor{seems like an API. They
  define the language behavior; grammar; values to static variables;
  the methods for each "class"(Object)...  These irregularities
  appears on engine implementation, maybe an wrong if statement and so
  on.} \Mar{Igor, avoid general discussion like $\leftarrow$this. look for
  explanation in some forum/tutorial and explain **when** you
  undertand the JS ecosystem design and can explain with confidence.}

\Mar{explain what is an **acceptable** incompatibilities. cite example
bug reports.}
\Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that
the function \CodeIn{Number.toPrecision(precision)}, in general,
if precision is defined the method returns a String 
containing the Number value represented either 
in decimal exponential notation or in decimal 
fixed notation~\cite{es6-toPrecision}. The Number object uses a 
property that the specification describes as approximately so when we use 
toPrecision with a bigger precision, the values of each engine may vary, this
could be considered as a case of incompatibility by engine
design.}\Mar{I don't understand the example very well and don't understand the
  relationship with HI/LO.}

@@

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases where the anomaly has
been detected in during the execution of test code or its close
%% the rationale we provide is related to the above; not crashes
neighborhood. The rationale is that the test in this group executed
without violating any internal checks of the API. In constrast,
warnings in the LO group reflect the cases where the anomaly was
observed during the execution of functions from standard JS libraries\Fix{check}.
  We found that different engines often check pre-conditions of
those functions differently. It can happen, for example, that one
engine enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
%% \Igor{these cases happen because the specification describes how a function
%% should work, however the internal implementation is defined by the
%% engine developers}\Mar{If you confirm that there is no code in specs
%%   (see comment above), what would be those abstract
%%   functions/interfaces that you mentioned to me the other day?}.
In those cases, our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the fuzzed test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only \Fix{12\%} of the reals bugs
we found originated from the LO category.

% I think this will make the definition of HI/LO weaker. We can
% elaborate this later. for example, in the evaluation.
%% \Igor{In addiction, we inserts in LO groups tests that generates a timeout warning
%% due the capacity of a fuzzer add an infinite repetition statement. We expected that
%% each test process can running utmost 5 seconds, if exceed this condition we stop 
%% the process and add a output message of a TIMEOUT error.}

\Igor{
  We defined if a warning is in HI or LO group according to console output.
  The error stream in the output shows relevant informations that we can 
  process. The Figure~\ref{fig:error-output} shows examples of HI and LO warning
  outputs based on the stream output came from Chakra engine. 
  % The error message shows informations related to the assertion code (see at line 2) 
  % that thows an Error exception. This case was considered as HI groups and after 
  % several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
}\Mar{igor, first add the real example then draft the discussion}

@@

\Mar{can we detect dups mining issue trackers?}
\Igor{
  acho que encontrar duplicatas seria um estudo a parte, devido a linguagem natural.
  Tenho umas consideracoes:
  \begin{itemize}
    \item warning HI possui a msg "Error: Test Failed", nao tem como buscar algo com isso, 
    se for pegar a linha que falhou, provavelmente vai mostrar a linha onde o assert se encontra.
    \item warning LO: podemos tentar conseguir buscar pelo output/funcao que falhou,
    \item O fuzzinator tem algo similar (dei uma olhada rapida, nao eh complicado)
  \end{itemize}
}\Mar{i think this is not the proper place to
  add this. discuss this with me.}
